Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-22 manuscript/climate_sensitivity_SI.Rmd
added footnote on fixed effect of year to tables S6 ans S7
closes #123

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). $R^2$ refers to conditional $R^2$.

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). $R^2$ refers to conditional $R^2$.

>>>>

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.019, 1999: -0.005; same values in all top models).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.03, 1999: 0.008; same values in all top models).

### 2020-07-22 manuscript/climate_sensitivity_draft.Rmd
added footnote on fixed effect of year to tables S6 ans S7
closes #123

Analyses focused on testing the predictions presented in Table 1 with $Rt$ as the response variable, and then repeated using $Rt_{ARIMA}$ as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented in the lme4 package in R [@R-lme4].
In the multi-year model, we included a random effect of tree nested within species and a fixed effect of drought year to represent the combined effects of differences in drought characteristics.
Individual year models included a random effect of species. 
All models included fixed effects of independent variables of interest (Tables 1,3) as specified below. 
We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016].

@@

Species traits (wood density, $LMA$, $PLA_{dry}$, and $\pi_{tlp}$) varied significantly among species (all p<0.05 in ANOVA; Table 2, Fig. **S4**).
Drought resistance also varied across species and by drought (Fig. **3**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).

>>>>

Analyses focused on testing the predictions presented in Table 1 with $Rt$ as the response variable, and then repeated using $Rt_{ARIMA}$ as the response variable. 
Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a mixed effects model, implemented in the lme4 package in R [@R-lme4].
In the multi-year model, we included a random effect of tree nested within species and a fixed effect of drought year to represent the combined effects of differences in drought characteristics.
Individual year models included a random effect of species. 
All models included fixed effects of independent variables of interest (Tables 1,3) as specified below.
All variables had variance inflation factors <1.5 (1 +/- 0.2). 
We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016].

@@

Species, as a factor in ANOVA, had significant influence (p<0.05) on all traits (wood density, $LMA$, $PLA_{dry}$, and $\pi_{tlp}$), with more significant pairwise differences for wood density and $PLA_{dry}$ than for $LMA$ and $\pi_{tlp}$ (Table 2, Fig. **S4**).
Drought resistance also varied across species, overall and in each drought year (Fig. **3**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).
